Learning and Recognition of \strips\ Action Models from State Observations

### 2018-01-20 doc/ijcai-18/observations-learning.tex
update to the likelihood function ijcai18 paper

According to the Bayes rule, the probability of an hypothesis $\mathcal{H}$ given the observations $\mathcal{O}$ can be computed with $P(\mathcal{H}|\mathcal{O})=\frac{P(\mathcal{O}|\mathcal{H})P(\mathcal{H})}{P(\mathcal{O})}$. In our scenario, the hypotheses are about the possible \strips\ action models that can be build given a set of operator headers, or in other words, given the $F_v(\xi)$ sets. Moreover, we assume that all the possible \strips\ action models are equiprobable so according to the Bayes rule $P(\mathcal{H}|\mathcal{O})$ is proportional to $P(\mathcal{O}|\mathcal{H})$. Finally, we assume that $P(\mathcal{O}|\mathcal{H})$ is given by the {\em observations  \strips\ edit distance}, mapping distances into probabilities (the larger the distance the lower the likelihood), according to the following sigmoid function $P(\mathcal{O}|\Xi)=\frac{1}{1+e^{-\delta(\Xi,\mathcal{O})}}$.

>>>>

According to the Bayes rule, the probability of an hypothesis $\mathcal{H}$ given the observations $\mathcal{O}$ can be computed with $P(\mathcal{H}|\mathcal{O})=\frac{P(\mathcal{O}|\mathcal{H})P(\mathcal{H})}{P(\mathcal{O})}$. In our scenario, the hypotheses are about the possible \strips\ action models that can be build given a set of operator headers, or in other words, given the $F_v(\xi)$ sets. Moreover, we assume that all the possible \strips\ action models are equiprobable so according to the Bayes rule $P(\mathcal{H}|\mathcal{O})$ is proportional to $P(\mathcal{O}|\mathcal{H})$. Finally, we assume that $P(\mathcal{O}|\mathcal{H})$ is given by the {\em observations  \strips\ edit distance}, mapping distances into probabilities (the larger the distance the lower the likelihood), according to the following expression $P(\mathcal{O}|\Xi)=1-\frac{\delta(\Xi,\mathcal{O})}{\delta(\Xi,*)}$.
